FoRTE baseline

### 2019-01-29 analysis/paper/paper.Rmd
PAPER: Start going through ED modules.

>>>>

## ED modules

(NOTE: Not a real section; just brainstorming notes for now)

- Big leaf model (no demographics) (`IBIGLEAF`)
    - Simplistic case
    - Only one PFT per patch (by definition). Can ask: Does it get the right one?
    - Compare fluxes against other cases.
- Branches (`IBRANCH_THERMO`)
    - Options:
        - (0) No branches in energy balance or biophysics
        - (1; default) Branches in energy balance, but not biophysics
        - (2) Branches in both
    - In theory, should be a minor component of the energy balance, so impact should be small. This is the hypothesis?
- Temperature variation of physiology (`IPHYSIOL`)
    - Options:
        - (0) Arrhenius function, `Gamma*` based on Foley et al. (1996) (TODO: REF)
        - (1) Arrhenius, `Gamma*` based on Michaelis-Mentel coefficients for CO2 and O2, as in Farquhar et al. (1980) (TODO: REF)
        - (2; default) Q10 equations and parameters of Collatz et al. (1991), with MM coefficients. High/low temperature correction in Moorcroft et al. (2001)
        - (3) As (2), but `Gamma*` as in Farquhar et al. (1980) and CLM.
    - Need to do some exploratory analysis here. Grab the relevant equations and coefficients and plot them (outside of ED) to compare behavior.
        - Possible angle: More important at temperature extremes?
    - Consult @rogers_2016_roadmap for inspiration
- Finite canopy radius (`CROWN_MOD`)
    - Options:
        - (0; default): Complete shading
        - (1): Finite canopy radius (Dietze 2008)
    - See current hypotheses
- Soil decomposition (`DECOMP_SCHEME`)
    - Options:
        - (0; default): Exponential
        - (1) Lloyd and Taylor (1994)
    - (1) requires additional parameters, so should increase parameteric uncertainty.
    - Hypothesis: Affects overall GPP/R~E~ balance, but not successional dynamics.
- Water limitation of photosynthesis (`H2O_PLANT_LIM`)
    - Options:
        - (0) No limitation.
        - (1; default): Supply is total soil water above wilting point integrated across all levels in rooting zone.
        - (2): Supply is total soil water at field capacity minus wilting point, scaled by "wilting factor":
          ```
          # k -- Soil layer
          # z -- Layer depth
          # psi -- Matric potential (for layer, or at wp or fc)
          # wp -- wilting point
          # fc -- field capacity
          (psi(k) - (H - z(k)) - psi_wp) / (psi_fc - psi_wp)
          ```
    - Sensitivity should depend on site climate and soil conditions.
    - UMBS are pretty wet sites, so shouldn't expect a huge effect.
- Structural growth (`ISTRUCT_GROWTH_SCHEME`)
    - Options:
        - (0; default) Use all `bstorage` (NSC?)
        - (1) Reserve `bstorage` to re-flush canopy and fine roots once before calculating structural growth.
    - (1) is a more conservative strategy, so should reduce the growth and relative dominance of early-successional PFTs. In particular, growth rate should decline more with size (because more LAI and fine roots means more reserves needed).
- Stomatal conductance model (`ISTOMATA_SCHEME`)
    - Options:
        - (0, default): Leuning
        - (1) Katul optimization model (see Xu et al. 2016 New Phyt.)
    - Need to read more about this...
- Trait plasticity (`TRAIT_PLASTICITY_SCHEME`)
    - Options:
        - (0, default): Static traits
        - (1) Vm0 (SLA) decrease (increase) with shading, based on Lloyd et al. (2010 Biogeosciences). Updated yearly.
        - (2) Same as (1), but updated monthly
        - (-1) Same as 1, but adjust SLA using height
        - (-2) Same as (2), but adjust SLA using height
    - If trait plasticity is optimal, this should reduce (?) the relative dominance of early-successional PFTs.
    - Probably introduces considerable predictive uncertainty, given new parameters for plasticity models.
- Other configs that ED has, but that we will probably ignore:
    - Allometry (`IALLOM`) -- Seems to mostly affect tropical PFTs. Worth checking.
    - Grass (`IGRASS`) -- I'm not running with any grass PFTs.
    - Phenology (`IPHEN_SCHEME`) -- Differences affect grasses and tropical species. Conifers are always evergreen, and hardwoods are always cold-deciduous (need to check that schemes are the same).
    - Seed dispersal (`REPRO_SCHEME`) -- Only seems to matter for multi-site runs, with some toggles for tropical (drought-deciduous) species.
    - Hydrodynamics (`PLANT_HYDRO_SCHEME`) -- Seems mostly tropics-focused? Look into the Xu et al. (2016; New Phyt.) paper.
